```{r}
library(ggplot2)

#start with small n
d1 <- data.frame(value=rnorm(20))
small_norm <- ggplot(d1, aes(x=value)) + geom_histogram()
print(small_norm)
```

### the above graph is of a low n normal distribution

### section below is code for low n binomial distribution

```{r}
d2 <- data.frame(value=rbinom(20, 20, 0.5))
small_binom <- ggplot(d2, aes(x=value)) + geom_histogram()
print(small_binom)
```

As we can see with the 2 graphs above. They do not look alike. \## Now we will transition to distribution with moderate-sized N \### The below graph and code is for a normal distribution

```{r}
d3 <- data.frame(value=rnorm(250))
mod_norm <- ggplot(d3, aes(x=value)) + geom_histogram()
print(mod_norm)
```

### The below graph and code is for a binomial distribution

Note how much more similar this graph is to the moderate-N normal relative to the small-N graphs.

```{r}
d4 <- data.frame(value=rbinom(250, 250, 0.5))
mod_binom <- ggplot(d4, aes(x=value)) + geom_histogram()
print(mod_binom)
```

## Finally, we will end with large values of N

### We will start with the normal distribution

```{r}
d5 <- data.frame(value=rnorm(2000))
large_norm <- ggplot(d5, aes(x=value)) + geom_histogram()
print(large_norm)
```

### And now the binomial distribution

Note how it is to the large-N normal distribution.

```{r}
d6 <- data.frame(value=rbinom(2000, 2000, 0.5))
large_binom <- ggplot(d6, aes(x=value)) + geom_histogram()
print(large_binom)
```
